Prestige bias in cultural evolutionary dynamics

### 2023-11-12 ms/ms.tex
update

\begin{figure}[H]
    \includegraphics[width=\linewidth]{ch_env.pdf}
  \caption{\textbf{Fixation probability in a changing environment.}
\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis). The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange). 
\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
When success bias is large ($1-\beta > 0.1$),  
simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}). With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak "selection" .
(\textbf{C,D}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias. 
When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
Markers show average of $10,000$ simulations, error bars show 75\% (panels A, C, and D) and 95\% (panel B) confidence intervals.
  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$ (panels A and B) and $A=0.8$ (panels C and D); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B, C, and D, the success-bias weight is $\alpha=0.1$.
  }
  \label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}	
  \label{fig:influence_advantage}
\end{figure}

>>>>

\begin{figure}[H]
    \includegraphics[width=\linewidth]{ch_env.pdf}
  \caption{\textbf{Fixation probability in a changing environment.}
\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis). The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange). 
\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
When success bias is large ($1-\beta > 0.1$),  
simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}). With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak "selection" .
(\textbf{C,D}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias. 
When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
Markers show average of $10,000$ simulations, error bars show 75\% (panels A, C, and D) and 95\% (panel B) confidence intervals.
  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$, $k=20$, $l=80$ (panels A and B) and $A=0.8$ (panels C and D); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B, C, and D, the success-bias weight is $\alpha=0.1$.
  }
  \label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here "Copier" of the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}	
  \label{fig:influence_advantage}
\end{figure}
